Information Sheet \\ {\large Learning Discrete Bayesian Networks from Continuous Data}

### 2015-12-04 information_sheet.tex
update info sheet

\title{Information Sheet \\ {\large Learning Discrete-valued Bayesian Networks from Mixed Data}}
\author{\normalsize Yi-Chun Chen, Tim A. Wheeler, Mykel J. Kochenderfer}
\date{}

@@

The proposed method learns discretization policies for continuous variables from mixed data while taking the Bayesian network structure into account.
Prior Bayesian methods, such as MODL \citep{Boulle_2006, Lustgarten_2011}, only consider the discretization of a single continuous variable with respect to another single discrete variable.
The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples.
The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.
Furthermore, empirical demonstrations show that the proposed method produces superior discretization policies, which was objectively evaluated using the cross-validated log-likelihood.\\[0em]

>>>>

\title{Information Sheet \\ {\large Learning Discrete Bayesian Networks from Continuous Data}}
\author{\normalsize Yi-Chun Chen, Tim A. Wheeler, Mykel J. Kochenderfer}
\date{}

@@

The proposed method learns discretization policies for continuous variables from continuous data while taking the Bayesian network structure into account.
Prior Bayesian methods, such as MODL \citep{Boulle_2006, Lustgarten_2011}, only consider the discretization of a single continuous variable with respect to another single discrete variable.
The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples for optimal discretization.
The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.
Furthermore, empirical demonstrations show that the proposed method produces superior discretization policies, which was objectively evaluated using the cross-validated log-likelihood.\\[0em]
